### 2024-03-27 paper/methods.qmd
table/plot output

After scraping, our corpus included the text of 22,390 comments and attachments for 20,787 distinct comments.  *[try reruning scraper sometime]*  By number of attachments, the median document had no attachments and the maximum number of attachments was 17.

## Sampling

@@

Further exploration — and a fortuitous coding error — identified a solution.  Using the `spaCy` natural language processing (NLP) suite and its R API `spacyR` *[versions]*, we analyzed the text of each document into individual words ("tokens") and classified each term's part of speech (noun, adjective, etc.).  Specifically, we applied dependency tagging, which enabled us to assemble adjective-noun bigrams (pairs of words), such as "public health" or "regulatory science."  *[filtering large and small docs; comment text and attachments concatenated]*

@@

At this point, [A1] brought the other collaborators into the project.  Without informing the other authors of the research question, all authors independently coded each comment in the sample as supporting or opposing ST, or too ambiguous to classify.  Krippendorff's alpha was used to assess inter-rater reliability *[https://link.springer.com/article/10.1007/s11135-004-8107-7]*; this statistic ranges from -1 to 1, with 1 indicating perfect agreement across all raters and 0 indicating "no agreement beyond chance" *[https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4974794/]*.  After an initial round of independent coding, Krippendorff's alpha was 0.86, with discordance on 74 / 814 comments.  We prepared a spreadsheet that contained only the discordance comments and each author's codes.  After discussing a few examples, each author separately reviewed the discordant comments, and submitted revised coding sheets.  After this one round of revision, Krippendorff's alpha was 0.94, with discordance on 32 / 814 comments.  Inspection of the remaining discordant comments suggested they were generally subject to reasonable disagreement.  For example, we disagreed about whether the following comment (EPA-HQ-OA-2018-0259-10925) should be classified as opposing ST or is too general and therefore irrelevant to ST:

@@

## Imputation

@@

@@

>>>>

After scraping, our corpus included the text of 22,390 comments and attachments for 20,787 distinct comments.  *[try reruning scraper sometime]*  We refer to this collection of comments and attachments as the *ST corpus*.  By number of attachments, the median document had no attachments and the maximum number of attachments was 17.

@@

### Sampling

Further exploration — and a serendipitous coding error — identified a solution to the oversampling challenge.  Using the `spaCy` natural language processing (NLP) suite and its R API `spacyR` *[versions]*, we analyzed the text of each document into individual words ("tokens") and classified each term's part of speech (noun, adjective, etc.).  Specifically, we applied dependency tagging, which enabled us to assemble adjective-noun bigrams (pairs of words), such as "public health" or "regulatory science."  *[filtering large and small docs; comment text and attachments concatenated]*

@@

### Manual coding

At this point, [A1] brought the other collaborators into the project.  Without informing the other authors of the research question, all authors independently coded each comment in the sample as supporting or opposing ST, or too ambiguous to classify.^[Among qualitative social scientists, this is referred to as "deductive coding." "Inductive" or "open" coding, by contrast, does not start with pre-defined codes, and is about developing a novel coding scheme, in a rather Baconian sense of induction.]  Krippendorff's alpha was used to assess inter-rater reliability *[https://link.springer.com/article/10.1007/s11135-004-8107-7]*; this statistic ranges from -1 to 1, with 1 indicating perfect agreement across all raters and 0 indicating "no agreement beyond chance" *[https://www.ncbi.nlm.nih.gov/pmc/articles/PMC4974794/]*.  After an initial round of independent coding, Krippendorff's alpha was 0.86, with discordance on 74 / 814 comments.  We prepared a spreadsheet that contained only the discordance comments and each author's codes.  After discussing a few examples, each author separately reviewed the discordant comments, and submitted revised coding sheets.  After this one round of revision, Krippendorff's alpha was 0.94, with discordance on 32 / 814 comments.  Inspection of the remaining discordant comments suggested they were generally subject to reasonable disagreement.  For example, we disagreed about whether the following comment (EPA-HQ-OA-2018-0259-10925) should be classified as opposing ST or is too general and therefore irrelevant to ST:

@@

### Imputation

@@

## Keyword synonyms and exclusions

Keyword detection is vulnerable to both false negatives (ignoring synonyms or closely-related concepts that do not strictly match chosen keywords) and false positives (counting unrelated concepts that do match chosen keywords).  For example, use of the rule's title, "Strengthening Transparency in Regulatory Science," should not count as evoking or referring to science.

To analyze the corpus for these possibilities, we implemented a lightweight variation on word embeddings.  Word embeddings attempt to represent words (or whatever unit of text) as vectors in an abstract space such that two vectors point in the same direction (more formally: have high cosine similarity) insofar as the corresponding words are semantically similar.  While word embeddings are usually created using neural network techniques, *[<https://proceedings.neurips.cc/paper/2014/hash/feab05aa91085b7a8012516bc3533958-Abstract.html>]* found that a less computationally-intensive method (partial singular value decomposition [SVD] of a pointwise mutual information matrix) produced similar results.  We implemented this method in R, following the example of *[Silge blogpost]*.

Specifically, we first filtered the spaCy annotated unigrams (from 20,787 comments) to those that were tagged as adjectives, nouns, verbs, and adverbs, since we judged these to be the most likely to contain keyword matches.  Tokens were defined as a combination of a word lemma (standardized word form) and part of speech tag, such as `scientifically_ADV`.  This resulted in 78,744 tokens.  Marginal occurrence probabilities (across the entire corpus annotated with spaCy) were calculated for each token.  Two tokens were determined to co-occur if they occurred in the same sentence (as identified by spaCy) in the same comment/attachment.  Co-occurrences were filtered at 20; that is, if a pair of tokens had 20 or fewer co-occurrences, this was treated as 0 co-occurrences.  After filtering, 8,364 tokens had at least one non-zero occurrence.  Co-occurrence / joint probabilities were calculated, and these were combined with marginal probabilities to calculate pointwise mutual information (pmi):

\[ pmi(x, y) = \log \frac{p(x, y)}{p(x) p(y) }\]

We then calculated the partial SVD of this pmi matrix using the `irlba` package *[version]*, selecting 256 dimensions.  This resulted in a 8,364 $\times$ 256 embedding matrix, with rows representing tokens and columns representing dimensions of the embedding space.

Given a keyword search string, such as `scien`, we first searched the embedding vocabulary (8,364 tokens) for matches.  For each match, identifying similar tokens was simply a matter of matrix multiplication and sorting.  The sorted results were filtered to have the same part of speech as the match, and then the top 5 results were displayed for each match.  We perused the resulting list to identify potential synonyms and matches that needed to be excluded.  Some additional, multiword false positive matches were identified based on our familiarity with the corpus, such as "Environmental Protection Agency" or the title of ST.

@@

## Inferential statistics and inductive scope

While the ST corpus can be considered a sample of US public opinion on ST, almost all comments come from a relatively highly engaged and haphazard subset:  people on email lists for environmental advocacy organizations, regulated industries, state regulators, readers of anti-environmentalist blogs.  It therefore cannot be considered a representative sample of anyone except "the kinds of people who were likely to have submitted comments on ST."  And for this population the ST corpus is, as it were, a nearly complete sample:  insofar as someone was likely to have submitted comments on ST, we probably have a comment from them in the ST corpus.

Thus, we believe that so-called inferential statistics — things like p-values from statistical hypothesis tests and confidence intervals — would be misleading, as they would incorrectly indicate that we can formally generalize from the ST corpus to some more-or-less well-defined larger population.  We therefore did not calculate, and do not report here, any such statistics.
